Browsernative Microservices

### 2017-02-28 paper.tex
pdf/tex build

As a primary source of comprehensive information this paper relies on
the work of Sam Newman{[}4{]} and the work of Fowler and Lewis{[}5{]}.
The purpose of this section is to gain confidence about the architecture
of microservices in the context of the browser platform.

@@

With an ever increasing complexity of single-page applications the
global nature of the DOM creates a daunting situation for code
organization and leads over times to highly fragmented bits of CSS and
obscured CSS selectors. Of course this situation dramatically lowers
code clarity and reusability. The only solution which will not break
with the existing global paradigm of the DOM is to allow separate pieces
of encapsulated code sit on top of the global DOM - introducing the
shadowed DOM approach.

@@

JS runs in a single-threaded language environment. Every script in the
browser environment, from handling UI events to query and process large
amounts of data or manipulating the DOM runs on a single thread{[}19{]}.
Putting a lot of work into the single main thread can slow down the web
service significantly. From time to time scripts can block or fail for
whatever reason which leads to a frozen or crashed UI. A worker can
overcome the bottleneck of the single-threaded nature with spawning new
\textbf{background threads} which allows the UI to stay responsive even
when computation-heavy tasks need to perform. Furthermore, a worker adds
a performance advantage embracing the multi core CPU architecture most
devices are running on today. To grasp the full potential of workers, a
reader might dive deeper into the Angular 2 architecture, where most of
the application layer is abstracted from the main rendering thread into
worker threads.\footnote{\href{https://docs.google.com/document/d/1M9FmT05Q6qpsjgvH1XvCm840yn2eWEg0PMskSQz7k4E}{Angular
  2 Rendering Architecture}}

@@

\KeywordTok{<script>}
  \KeywordTok{class} \NormalTok{SignInStyling }\KeywordTok{extends} \NormalTok{HTMLElement }\OperatorTok{\{}
    \AttributeTok{constructor}\NormalTok{() }\OperatorTok{\{}
      \KeywordTok{super}\NormalTok{()}\OperatorTok{;}
      \KeywordTok{this}\NormalTok{.}\AttributeTok{attachShadow}\NormalTok{(}\OperatorTok{\{}\DataTypeTok{mode}\OperatorTok{:} \StringTok{'open'}\OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
      \KeywordTok{this}\NormalTok{.}\VariableTok{shadowRoot}\NormalTok{.}\AttributeTok{appendChild}\NormalTok{(}\VariableTok{temp}\NormalTok{.}\AttributeTok{content}\NormalTok{)}\OperatorTok{;}
      \CommentTok{// f.e. append templates according to window.innerWidth}
      \CommentTok{// style related JS altering}
      \CommentTok{// this.getAttribute('theme') for configuration}
    \OperatorTok{\}}
    \AttributeTok{attributeChangedCallback}\NormalTok{(attrName}\OperatorTok{,} \NormalTok{oldVal}\OperatorTok{,} \NormalTok{newVal) }\OperatorTok{\{}
      \CommentTok{// react on changing attributes}
    \OperatorTok{\}}
  \OperatorTok{\}}
  \VariableTok{customElements}\NormalTok{.}\AttributeTok{define}\NormalTok{(}\StringTok{'sign-in-styling'}\OperatorTok{,} \NormalTok{SignInStyling)}\OperatorTok{;}
\OperatorTok{<}\SpecialStringTok{/script>}
\end{Highlighting}
\end{Shaded}

As mentioned before, HTML templates provide an opportunity to define
\textbf{CSS modules}. Tags like \texttt{\textless{}style\textgreater{}}
and \texttt{\textless{}slot\textgreater{}} create a kind of stencil
filled by content from the \texttt{index.html}. As it is possible to
expand templates in place it could also be possible to define
\textbf{template components} like the \texttt{mobile-template} to
atomize the component further and to increase code brevity.

>>>>

As a primary source of comprehensive information this paper relies on
the work of Sam Newman{[}4{]} and the work of Fowler and Lewis{[}5{]}.
The purpose of this section is to develop confidence about the
architecture of microservices in the context of the browser platform.

@@

With an ever increasing complexity of single-page applications the
global nature of the DOM creates a daunting situation for code
organization and leads over times to highly fragmented bits of CSS or
obscured CSS selectors. Of course this situation dramatically lowers
code clarity and reusability. The only solution which will not break
with the existing global paradigm of the DOM is to allow separate pieces
of encapsulated code sit on top of the global DOM - introducing the
shadowed DOM approach.

@@

JS runs in a single-threaded language environment. Every script in the
browser environment, from handling UI events to query and process large
amounts of data or manipulating the DOM runs on a single thread{[}19{]}.
Putting a lot of work into the single main thread can slow down the web
service significantly. From time to time scripts can block or fail for
whatever reason which leads to a frozen or crashed UI. A worker can
overcome the bottleneck of the single-threaded nature with spawning new
\textbf{background threads} which allows the UI to stay responsive even
when computation-heavy tasks need to perform. Furthermore, a worker adds
a performance advantage embracing the multi core CPU architecture most
devices are running on today. To grasp the full potential of workers, a
reader might dive deeper into the Angular 2 architecture, where most of
the application layer is abstracted from the main rendering thread into
worker threads.{[}\^{}Jbanov{]}

@@

\KeywordTok{<script>}
  \KeywordTok{class} \NormalTok{SignInStyling }\KeywordTok{extends} \NormalTok{HTMLElement }\OperatorTok{\{}
    \AttributeTok{constructor}\NormalTok{() }\OperatorTok{\{}
      \KeywordTok{super}\NormalTok{()}\OperatorTok{;}
      \KeywordTok{this}\NormalTok{.}\AttributeTok{attachShadow}\NormalTok{(}\OperatorTok{\{}\DataTypeTok{mode}\OperatorTok{:} \StringTok{'open'}\OperatorTok{\}}\NormalTok{)}\OperatorTok{;}
      \ControlFlowTok{if} \NormalTok{(}\VariableTok{window}\NormalTok{.}\AttributeTok{innerWidth} \OperatorTok{>} \DecValTok{1280}\NormalTok{) }\OperatorTok{\{}
        \KeywordTok{const} \NormalTok{temp }\OperatorTok{=} \KeywordTok{this}\NormalTok{.}\AttributeTok{querySelector}\NormalTok{(}\StringTok{'#highres'}\NormalTok{)}\OperatorTok{;}
        \KeywordTok{this}\NormalTok{.}\VariableTok{shadowRoot}\NormalTok{.}\AttributeTok{appendChild}\NormalTok{(}\VariableTok{temp}\NormalTok{.}\AttributeTok{content}\NormalTok{)}\OperatorTok{;}
      \OperatorTok{\}}  
      \CommentTok{// this.getAttribute('theme') for configuration}
      \CommentTok{// selecting nodes for altering}
    \OperatorTok{\}}
    \AttributeTok{attributeChangedCallback}\NormalTok{(attrName}\OperatorTok{,} \NormalTok{oldVal}\OperatorTok{,} \NormalTok{newVal) }\OperatorTok{\{}
      \CommentTok{// react on changing attributes}
    \OperatorTok{\}}
  \OperatorTok{\}}
  \VariableTok{customElements}\NormalTok{.}\AttributeTok{define}\NormalTok{(}\StringTok{'sign-in-styling'}\OperatorTok{,} \NormalTok{SignInStyling)}\OperatorTok{;}
\OperatorTok{<}\SpecialStringTok{/script>}
\end{Highlighting}
\end{Shaded}

As mentioned before, HTML templates provide an opportunity to define
\textbf{CSS modules}. Tags like \texttt{\textless{}style\textgreater{}}
and \texttt{\textless{}slot\textgreater{}} create a kind of stencil
filled by content from the \texttt{index.html}. As it is possible to
expand templates in place it could also be possible to define
\textbf{template components} like the \texttt{mobile-template.html} to
atomize the component further and to increase code brevity.
